From Archives to AI: Residential Property Data Across Three Decades in Brunei Darussalam

### 2025-01-16 manuscript.qmd
For submission

Each webpage displayed a fixed number of listings (e.g. 128 per page). 
To scrape all pages, a loop was created to iterate through each page by modifying the URL (such as with an `&offset=<number>` parameter, where `<number>` represented the cumulative number of listings already scraped).

>>>>

Each webpage displayed a fixed number of listings (e.g. 128 per page). 
To scrape all pages, a loop was created to iterate through each page by modifying the URL (such as with an `&offset=<number>` parameter, where `<number>` represents the cumulative number of listings already scraped).
